\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/iteration1.tex
marked changes

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and pleasurable. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition.

>>>>

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, \changes{IR selection was perceived to be more direct and pleasurable. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}, and many participants compared the overall time of target acquisition.}
